---
title: "foofactors for Stat 547"
author: "Poushali Maji"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

'Foofactors' is a homework package for stat 547 that helps manipulate factors. Here are some examples using the Iris dataframe and factor Species. 

## Bind two factors

Bind 2 factors together using the function **fbind**

```{r}
library(foofactors)
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
```

## Get the frequency of factor levels

Tabulate the levels in a factor

```{r}
freq_out(iris$Species)
```

## Test whether a factor should a factor or character 

This test depends on whether the factor has more observations than levels: if the number of unique values is equal to the number of observations, the function returns FALSE, i.e. the factor should really be a character. 

```{r}
fctr_or_chr(iris$Species)

nlevels(iris$Species)
length(iris$Species)
#See?
